Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data

### 2024-01-25 paper1.Rmd
change

---
title: "Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data"
author: 
  - Ziyi Liu
thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This study presents a comprehensive analysis of public health inspection data from Toronto's BodySafe program, aiming to evaluate the safety standards to personal service in the city. We examine the trends in public health standards including spas, salons and tatto parlors. We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions. By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation. This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: reference.bib
---

@@

plot_data <- as.data.frame(table(data$srvType, data$insStatus))

@@

data <- read.csv("toronto_bodysafe.csv")

# Convert the 'insDate' column to a Date type
data$insDate <- ymd(data$insDate)

@@

# Plotting the data
ggplot(monthly_inspection_data, aes(x = month, y = n)) +
  geom_line(color = 'teal') +
  geom_point(color = 'darkblue') +
  labs(title = 'Number of Inspections Over Time in Toronto BodySafe Establishments',
       x = 'Date (Month-Year)',
       y = 'Number of Inspections') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

---
title: "Evaluating Public Health Standards in Toronto: An Analysis of BodySafe Inspection Data"
author: 
  - Ziyi Liu
thanks: "Code and data are available at: https://github.com/liuziy23/Ziyi-Liu.git"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This study presents a comprehensive analysis of public health inspection data from Toronto's BodySafe program, aiming to evaluate the safety standards to personal service in the city. We examine the trends in public health standards including spas, salons and tatto parlors. We focuses on infraction categories, inspection outcomes, and the impact of enforcement actions. By investigating the correlation between service types, inspection results, and geographic distribution, this study provides insights of effectiveness of public health policies and the implementation. This paper not onlt focus on the effectiveness of BodySafe program but also investigating potential opportunities to enhance public health safety."
output: pdf_document
toc: TRUE
bibliography: reference.bib
---

@@

data <- utils::read.csv("toronto_bodysafe.csv")
plot_data <- utils::as.data.frame(utils::table(data$srvType, data$insStatus))

@@

data <- read.csv("toronto_bodysafe.csv")
# Convert the 'insDate' column to a Date type
data$insDate <- ymd(data$insDate)

@@

# Plotting the data
ggplot(monthly_inspection_data, aes(x = month, y = n)) +
  geom_line(color = '#008080') +  
  geom_point(color = 'darkblue') +
  labs(title = 'Number of Inspections Over Time in Toronto BodySafe Establishments',
       x = 'Date (Month-Year)',
       y = 'Number of Inspections') +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The graph shows fluctuations in the number of inspections conducted over time in Toronto's Bodysafe establishments. Also, the data is added every month and offers the insight into trends and patterns of the frequency of inspections.The reason for these fluctuations are possibily due to policy changes, resource ability and seasonal variations. The peaks in the graph also indicate the months that have higher number of inspections. These might correspond to increase in regulatory activity or specific campaigns. In addition, the period where has less inspections indicate less activities due to holidays [@cite1].
